### 2012-10-24 inst/examples/reed-example.Rmd
getting useless boundary solution when maximizing likelihood over sigma_n ... hmm

```{r}
minusloglik <- function(par){
  gp <- gp_fit(obs, X, c(sigma_n=1, l=par))
  -gp$llik
}
minusloglik(1)
o <- optimize(minusloglik, c(0,100))
o
hyperpars <- c(sigma_n=1, l=o$objective)
```

>>>>

```{r}
minusloglik <- function(par){
  gp <- gp_fit(obs, X, c(sigma_n=par, l=1))
  -gp$llik
}
minusloglik(1)
o <- optimize(minusloglik, c(0,150))
o
hyperpars <- c(sigma_n=o$minimum, l=1)
```
